In this section we will describe our methodology. At a hight level our main activities will be: review the literature, elaborate a conceptual model, implement and evaluate a middleware, write the dissertation, write paper and viva presentation.
The implementation will be divided in 2 phases so we can submit intermediate results to scientific conferences.

\begin{enumerate}

\item \emph{literature review}

First we will conduct a literature review with the objective to find all the relevant related works, what is the state of the art, review that works and better proposition our proposal in relation to that works.

\item \emph{elaborate a conceptual model and architecture}

In parallel to the literature review, we will develop a conceptual model to integrate Goal-Oriented Requirements Engineering, Architecture-Based Self-Adaptation so that the system goals can be traced to architecture modules at runtime. This conceptual-model will describe the Architectural components of the proposed architecture, their relations, how this elements are related to the goal model that they implement and how this model can be manipulated at runtime.


\item \emph{implement and validate a middleware (Core)}

At this stage we will implement the core of a middleware to support execution of components as described by the proposed conceptual model and evaluate. To do the evaluation we will specify and describe a study case system and implement the system using the middleware and the proposed architecture.

\item \emph{write paper about the middleware (Core)}

We will report the results of the middleware implementation and validation as a paper.

%\item \emph{implement and validate evolution capacities in the middleware}

%implement and evaluate strategies for runtime strategies incorporation. Report the results.

%\item \emph{implement and validate multi-agent strategies}

 %implement and evaluate strategies for support communication and discovery of agents (multi-agent) as a support for open-systems. Report the results.

\item \emph{implement and validate dependability strategies}

 implement and evaluate GODA\cite{mendonca_dependability_2015} strategy for runtime dependability analysis at runtime.

 \item \emph{write paper about dependability strategies}

 We will report the results of the middleware implementation and validation as a paper.

\item \emph{write up dissertation}

gather all intermediate results and format as a dissertation.

\item \emph{viva}

present the dissertation.

\end{enumerate}
