%\section{Research Questions}

% is there any component model suitable to trace goals and component service.

In order to allow the system make decisions about its structure based on requirements and context we need a model that can correlate these three concepts: the system structure, the goals and the execution context.

% What leads us to or research question:


\setlength{\fboxsep}{10pt}
\noindent\fbox{%
    \parbox{0.95\textwidth}{%
        \textbf{Research Question 1 (RQ1):} What would be a good model of software system that
        could allow one to reason about the system structure, context and trace the goals at runtime? In other words, how to represent the system goals, architectural structure, operation context and their relationship?
    }%
}\bigskip
Previous work in the literature \cite{pessoa_dependable_2015} have partially tackled this research question. However, our major concern here relates to the traceability between goals and tasks, software architectural components and the context of operation.

To develop what would be a good model we address further questions in relation to the fitness of the model for the purpose of deciding on system adaptations. First of all, we want to realize a valid deployment of the system:

\setlength{\fboxsep}{10pt}
\noindent\fbox{%
    \parbox{0.95\textwidth}{%
        \textbf{Research Question 2 (RQ2):} How to, using the model from RQ1, deploy a Self-Adaptive System that is dependable in face of context variability? % verify if systems goals are achievable at runtime in face of deployment (configuration) uncertainty.

    }%
}\bigskip

Beside checking the system validity in other to predict system dependability, we want to be able to tolerate faults at runtime. This leads us to the next research question:

\setlength{\fboxsep}{10pt}
\noindent\fbox{%
    \parbox{0.95\textwidth}{%
        \textbf{Research Question 3 (RQ3):} How to guarantee that the systems is dependable in face of error prone components at runtime?
        % assure that goals are always achieved, if they are achievable, in face of components faults ?
    }%
}\bigskip

% This research question is the search to insert fault-tolerance.
